\documentclass[a4paper]{article}
\usepackage{lipsum}
\usepackage{url}
\usepackage{graphicx}
\usepackage[margin=2cm]{geometry}
\graphicspath{ {images/} }

\begin{document}

\subparagraph{25th October}
Recap of the submitted project proposal. \\
Discussed the lack of proposed methodology in the proposal, due to competition framework not being researched fully. Agreed to have a stronger idea with the interim report. \\
Overview for the next stage of the work plan, researching and understanding the GVGAI Framework --- specifically looking into the Learning track. \\
Agreed to meet on Wednesdays 2--2:30 as required.

\subparagraph{14th November}
Progress report. \\
Created a keyboard controller interface to play games. \\
Created a random agent and a way to run this on all 100 games to provide a comparison point. \\
Unable to run previous agents as none are available from the new framework although some may be available soon. \\
Could run a baseline learning implementation as discussed although this will take some time to implement and run. \\
Current research is going well ready to start work on the interim report specifically background research. \\
Will look into overleaf for sharing of the interim report drafts.

\subparagraph{11th January}
Direction the project is heading after the preliminary research looking into applying the RL algorithms in the OpenAI Baseline package to the problem. \\
Current work involving refactoring to use the given agent structure. \\
Need to install the OpenAI Baseline package and implement it for a single game, this should be finished early February. \\
Meet in early February when results from implementing the package on a single game. \\
Looking into journals and conferences other work has been published in to get an idea for publishing the final paper produced. \\

\end{document}
